Global case

### 2025-05-14 lipschitz 2025/Lipitschz.tex
update

	The accurate constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (together with$\hat{x}'_i=\ReLU(x'_i)$) are the follows:
	\begin{align*}
		& \begin{aligned}
			y_i + x'_i &\leq a\beta_i        &\quad\quad
			y_i + x'_i &\geq (1-a)\alpha_i \\
			x'_i       &\leq a'\beta_i       & 
			x'_i       &\geq (1-a')\alpha_i \\
			\hat{y}_i  &\leq a\gamma_i       &
			\hat{y}_i  &\geq -a'\gamma_i \\
			\hat{y}_i  &\leq y_i + (1-a)\gamma_i  &
			\hat{y}_i  &\geq y_i - (1-a')\gamma_i \\
			\hat{y}_i  &\leq -x'_i + a\beta_i &
			\hat{y}_i  &\geq -x'_i + (1-a')\alpha_i \\
			\hat{y}_i  &\leq y_i + x'_i + (1-a)(-\alpha_i) &
			\hat{y}_i  &\geq y_i + x'_i + a'(-\beta_i)
		\end{aligned}
	\end{align*} Here, $a,a'$ are the binary variables, and $a'$ also play the role of binary variable for $\hat{x}'_i=\ReLU(x'_i)$. The constraints for $x_i$s are not necessary, or at least their MILP constraints can be relaxed to LP without reducing accuracy.

@@

	\section{Experiments}

>>>>

	Given $\gamma_i$ as the upper bound of $y_i$, $\alpha_i,\beta_i$ be the upper and lower bound of $x_i,x_i'$, 
	the accurate constraints for $\hat{y}_i = \ReLU(x'_i+y_i)-\ReLU(x'_i)$ (together with $\hat{x}'_i=\ReLU(x'_i)$) are the follows:
	\begin{align*}
		& \begin{aligned}
			y_i + x'_i &\leq a\beta_i        &\quad\quad
			y_i + x'_i &\geq (1-a)\alpha_i \\
			x'_i       &\leq a'\beta_i       & 
			x'_i       &\geq (1-a')\alpha_i \\
			\hat{y}_i  &\leq a\gamma_i       &
			\hat{y}_i  &\geq -a'\gamma_i \\
			\hat{y}_i  &\leq y_i + (1-a)\gamma_i  &
			\hat{y}_i  &\geq y_i - (1-a')\gamma_i \\
			\hat{y}_i  &\leq -x'_i + a\beta_i &
			\hat{y}_i  &\geq -x'_i + (1-a')\alpha_i \\
			\hat{y}_i  &\leq y_i + x'_i + (1-a)(-\alpha_i) &
			\hat{y}_i  &\geq y_i + x'_i + a'(-\beta_i)
		\end{aligned}
	\end{align*} Here, $a,a'$ are the binary variables, and $a'$ also play the role of binary variable for $\hat{x}'_i=\ReLU(x'_i)$. The constraints for $x_i$s are not necessary, or at least their MILP constraints can be relaxed to LP without reducing accuracy.

@@

	\section{Experimental Evaluation}

	We implemented our code in Python 3.8.
	Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD Threadripper 7970X  ($32$ cores$@4.0$GHz) with 256 GB of main memory and 2 NVIDIA RTX 4090.

	We will do experiments on two networks for MNIST dataset and another physical model.

	Among two MNIST $5\times 100$  full-connected DNN, one is a normally trained neural network and another is for trained for adversarial robustness. We call them MNIST $5\times100$-normal and MNIST $5\times 100$-DiffAI. They have the same structure: 5 hidden layer with 100 neurons each, 10 outputs and 784 inputs.

	The physical network is a simplified model with 10 input neurons, 26 output neurons, and 2 hidden layers with 50 neurons each.

	\subsection{Comparison of different modelings}

	\subsection{Comparison of different scoring algorithms}
